\vspace{-2.5em} Ad-Hoc Coordinate Change Algorithm For The Split-Aperture\\ Polarization Microscope \vspace{-1em}

### 2017-10-16 notes/2017-10-03-split-aperture-coordinate-change/report/report.tex
Split aperture test data reconstruction.

%%%%%%%%%%%%
% Document %
%%%%%%%%%%%%
\begin{document}
\title{\vspace{-2.5em} Ad-Hoc Coordinate Change Algorithm For The Split-Aperture\\
  Polarization Microscope \vspace{-1em}} \author{Talon
  Chandler}% and Patrick La Rivi\`ere}
\date{\vspace{-1em}\today\vspace{-1em}}
\maketitle
\section{Introduction}
The split-aperture polarization microscope can measure the azimuth orientation
of a single dipole in two rotated views. These notes describe an algorithm for
converting noise-corrupted azimuth orientations in two rotated views into the
azimuth and inclination orientation. We define the coordinates, outline the
algorithm, then show the error in the estimate with noise-free and noise-corrupted
measurements.

@@

\section{Results}
I used $\alpha = 30^{\circ}$ for all tests.

@@

\fig{../figures/recon-error-gauss.pdf}{.9}{Error in the estimate with
  noise-corrupted data. I assumed that the two azimuth angle measurements had normally distributed noise with $\mu = 0$ and $\sigma = 2^{\circ}$.}{results}
\end{document}

>>>>

%%%%%%%%%%%%
% Document %
%%%%%%%%%%%%
\begin{document}
\title{\vspace{-2.5em} Ad-Hoc Coordinate Change Algorithm For The Split-Aperture\\
  Polarization Microscope \vspace{-1em}} \author{Talon
  Chandler}% and Patrick La Rivi\`ere}
\date{\vspace{-1em}October 3, 2017\\(Last Updated: \today)\vspace{-1em}}
\maketitle
\section{Introduction}
The split-aperture polarization microscope can measure the azimuth orientation
of a single dipole in two rotated views. These notes describe an algorithm for
converting noise-corrupted azimuth orientations in two rotated views into the
azimuth and inclination orientation. We define the coordinates, outline the
algorithm, then show the error in the estimate with noise-free and noise-corrupted
measurements. Finally, we test the algorithm on a set of single-molecule data.

@@

\section{Accuracy Results}
I used $\alpha = 30^{\circ}$ for all tests.

@@

\fig{../figures/recon-error-gauss.pdf}{.9}{Error in the estimate with
  noise-corrupted data. I assumed that the two azimuth angle measurements had normally distributed noise with $\mu = 0$ and $\sigma = 2^{\circ}$.}{results}
\pagebreak

\section{Test Data Results}
Tomomi supplied five frames of test data in a \texttt{.xlsx} file. Each frame
had $\sim$40 single molecules with its x-y position and its azimuthal angle from
each view.

I used the algorithm detailed above to calculate the coordinates in the
laboratory frame (see Figure 1a)) then plotted the orientations and positions of
the molecules in Figures 4-8. The origin is marked by a dot in the top corner. The
data was supplied without units, so the scale bar may be in units of $\mu$m or
pixels.

\fig{../test-analysis/output/frame01.pdf}{.4}{Frame 1.}{results}
\fig{../test-analysis/output/frame02.pdf}{.4}{Frame 2.}{results}
\fig{../test-analysis/output/frame03.pdf}{.4}{Frame 3.}{results}
\fig{../test-analysis/output/frame04.pdf}{.4}{Frame 4.}{results}
\fig{../test-analysis/output/frame05.pdf}{.4}{Frame 5.}{results}

\end{document}
